\documentclass[11pt,letterpaper]{article}

\usepackage{graphicx}
\usepackage{fancybox}
\usepackage[utf8]{inputenc}
\usepackage{epsfig,graphicx}
\usepackage{multicol,pst-plot}
\usepackage{pstricks}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage{upgreek}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=1cm]{geometry}
\usepackage{tcolorbox}
\usepackage{import}
\pagestyle{empty}
\DeclareMathOperator{\tr}{Tr}
\renewcommand{\sp}[1]{$${\begin{split}#1\end{split}}$$}

\usepackage{lipsum}
\usepackage{mdframed}
\usepackage{listings}
\usepackage{color}

% Margins
% \topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in
 % The problem environment introduced.                                     
\newenvironment{problem}[2][Problem]                                  
        {\begin{tcolorbox}[colback=white,colframe=gray!50,title=#1 #2]}
        {\end{tcolorbox}}
        % {\begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
        % {\end{mdframed}}
% Define solution environment
\newenvironment{solution}                      
        {\begin{mdframed}\textit{Solution:} \\}
        {\end{mdframed}}
% Define an environments for proofs
\newenvironment{myproof} 
        {\textit{Proof:}}                                   
        {\begin{flushright} Q.E.D. \end{flushright}}
% Define a theorem environment and a notation one too
\newenvironment{mytheorem}                    
        {\begin{mdframed}\textbf{Theorem:} \\}
        {\end{mdframed}}
\newenvironment{notation}                      
        {\begin{mdframed}\textit{Notation:} \\}
        {\end{mdframed}}
% A new example wouldnt so any harm either...  
\newenvironment{example}                             
        {\textit{Example:}\\}
	{}
%I sholud be ashamed to forget the definition environment(He forgot this he dumb haha)
\newenvironment{definition}
	{\begin{mdframed}$\underline{\textit{Def}^\textit{n}:} $\\}
	{\end{mdframed}}
%Corollary envvvvvvvvv
\newenvironment{corollary}
	{\textbf{Corrolary:}\\}

\pagestyle{empty}

\begin{document}

\begin{center}
  \Huge{Computer Networks Notes}\\
  \vspace{0.25cm}
  \small{Anant Srivastava}
\end{center}

\vspace{-1.75cm}

\begin{flushright}
  Instructor: \\ Mrs. Shubhani Agarwal
\end{flushright}

\vspace{-1.3cm}

\begin{flushleft}
  B.Tech. CSE
\end{flushleft}

\rule{15.5cm}{0.1mm}%{\linewidth}{0.1mm}

% Optional TOC
\tableofcontents
\pagebreak

%--Paper--

\section{Computer Networks}

\subsection{Data Communication:}

the exchange of information between two devices via some form of transmission medium, such as wired cable. The 4 fundamental characteristics of this are:
\begin{itemize}
  \item Delivery
  \item Accuracy
  \item Time
  \item Jitter (variation in packet delivery time)
\end{itemize}

\subsection{Components of data communication:}
There are 5 components in data communication: 
\begin{itemize}
  \item Sender
  \item Reciever
  \item Message (the data to be transferred)
  \item Transmission medium
  \item Protocol(the rules and regulations to be send)
\end{itemize}

\subsection{Data representation:}
how we can represent data. It represents in the form of text, numbers, image, audio and video.

\subsection{Components of CN:}
There are 5 types of data flow: 
\begin{itemize}
\item IP address
  
  The node address connected to a network for communication.
\item Node 
	
  Connection point inside a network that can recieve or that can send or store data. 
\item Router
  
  It is physical device that sends in datapackets between networks.
\item Switch
  
  Device that connects other devices and manages node to node communication.
  \begin{itemize}
  \item 1.Circuit Switching 
  \item 2.Message Switching
  \item 3.Packet Switching
  \end{itemize}
\item Newtwork cable
  \begin{itemize}
  \item 1.Coaxial cable
  \item 2.Twisted cable
  \item 3.Optic fibre cable
  \end{itemize} 
\end{itemize}

\subsection{Data flow:}
There are 3 types of data flow: 
\begin{itemize}
\item Simplex
 	
  One way: sender stays sender and reciever stays reciever. 
	Unidirectional. 
\item Half-Duplex
	
  The direction can be changed but at a time there can only be one directional travel.
	Each station can both transmit and receive but not at the  same time. 
\item Duplex
	
  Simultaneous Data transfer over both nodes. 
	Both stations can transmit and receive simultaneously. 
\end{itemize}

\subsection{Goals of Computer Networks:}
Network is a set of devices connected by communication links. A network must be able to meet a certain number of criteria. These are:
\begin{itemize}
  \item Resource Sharing
  \item High Reliability
  \item flexible access
  \item Scalability
  \item Network Performance
  \item Saving Money
\end{itemize}

\subsection{Types of CN:}
There are 3 types of data flow: 
\begin{itemize}
\item LAN(Local Area Network)
 	
  It Connects over a short distance.
\item MAN (Metropolitan area network)
  
 It is larger than then LAN but smaller than WAN.
\item WAN(Wide Area Network)
	
  Connects computers over a Wide area. 
\end{itemize}

\subsection{OSI model}
\begin{enumerate}
  \item Physical layer\\
    It is either Analog or Digital.\\
    It is a kind of continuous wave form that changes over time. 
    What matters in this is:
    For Analog:
    \begin{itemize}
      \item Amplitude
      \item Frequency
      \item Phase
    \end{itemize}
    For Digital:
    \begin{itemize}
      \item Bitrate
      \item Bit interval
    \end{itemize}
\end{enumerate}

\subsection{Layers of OSI model}

\end{document}
